The investment strategy based on behavior of artificial earthworm for use in algotrading

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
procedure -> approach

Let's consider an artificial earthworm, which behaves like its natural inspirer. Let this artificial worm have a length of $p1$ candles (vectors representing the knowledge about events occurring within the contractual part of the time series). Let her movement come down to the successive ,,eating'' one candle and simultaneous ,,discarding'' of one candle --- always having $p1$ candles. Thus the earthworm moves incrementally at length of time called the period of the candle. $i-th$ candle is  defined as a row of data of values  $O_i$, $H_i$, $L_i$, $C_i$ (Open, High, Low and Close). These values represent (in order): the value at the beginning of this period, the maximum value within the period, the minimum and the closing values - at the end of the candle.\\
Let's assume that candle can have color (often in a number of brokerage platforms, this procedure is used). Therefore candles may be red (when the opening of the candle is higher than its closing $O_i>C_i$) and green (when the situation is opposite $O_i<C_i$).\\
Let's also assume --- it is a primary strategy rule - that when an artificial earthworm has a significant advantage of red candles, a short position is opened or continued. When earthworm has the significant advantage of green candles, a long position is opened or continued. Imprecise term ,,significant'' is defined by the use of the second parameter p2 according to the rules:
\begin{equation}
\text{If }  Lr > p1/2 -p2 \text{ then } short;
\end{equation}
opening of short position will be suggested;
\begin{equation}
\text{If }  Lg > p1/2 -p2 \text{ then } long;
\end{equation}
opening of long position will be suggested;
\begin{equation}
\text{If }  Lg < p1/2 -p2 \text{ and } Lr< p1/2-p2 \text{ then } none;
\label{eq:eq3}
\end{equation}
the continuation of state will be suggested (position or no opened position).\\

>>>>

Let's consider an artificial earthworm, which behaves like its natural inspirer. Let this artificial worm have a length of $p1$ candles (vectors representing the knowledge about events occurring within the contractual part of the time series). Let her movement come down to the successive ,,eating'' one candle and simultaneous ,,discarding'' of one candle --- always having $p1$ candles. Thus the earthworm moves incrementally at length of time called the period of the candle. $i-th$ candle is  defined as a row of data of values  $O_i$, $H_i$, $L_i$, $C_i$ (Open, High, Low and Close). These values represent (in order): the value at the beginning of this period, the maximum value within the period, the minimum and the closing values - at the end of the candle.\\
Let's assume that candle can have color (often in a number of brokerage platforms, this approach is used). Therefore candles may be red (when the opening of the candle is higher than its closing $O_i>C_i$) and green (when the situation is opposite $O_i<C_i$).\\
Let's also assume --- it is a primary strategy rule - that when an artificial earthworm has a significant advantage of red candles, a short position is opened or continued. When earthworm has the significant advantage of green candles, a long position is opened or continued. Imprecise term ,,significant'' is defined by the use of the second parameter p2 according to the rules:
\begin{equation}
\text{If }  Lr > p1/2 -p2 \text{ then } short;
\end{equation}
opening of short position will be suggested;
\begin{equation}
\text{If }  Lg > p1/2 -p2 \text{ then } long;
\end{equation}
opening of long position will be suggested;
\begin{equation}
\text{If }  Lg < p1/2 -p2 \text{ and } Lr< p1/2-p2 \text{ then } none;
\label{eq:eq3}
\end{equation}
the continuation of state will be suggested (position or no opened position).\\
